\LARGE \bf Cascading Situation Assessment for Robots

### 2017-02-27 paper.tex
Proof-reading part 1

\author{Séverin Lemaignan$^{1}$, Fotios Papadopoulos$^{1}$%
\thanks{$^{1}$Authors are with Centre for Robotics and Neural Systems,
        Plymouth University, Plymouth PL48AA, United Kingdom
        {\tt\small firstname.surname@plymouth.ac.uk}}%
}

@@

\uwds is a distributed and lightweight open-source
framework\footnote{\url{https://github.com/severin-lemaignan/underworlds}} that
enables robot programmers to build and refine in real-time spatial and temporal
models of the environment surrounding a robot. \uwds make it possible to share
these world models amongst the software components running on the robot.
Critically, \uwds permits to represent and manipulate in a distributed manner
\emph{multiple alternatives} to the current, perceived world model: for
instance, the world with some objects filtered out, the world `viewed' from the
perspective of another agent, an hypothetical world resulting from the simulated
application of a plan, etc.

\subsection{Situation Assessment}

@@

\uwds is specifically inspired by the geometric and temporal reasoning module
{\sc Spark} (\emph{SPAtial Reasoning \& Knowledge}~\cite{sisbot2011situation}.
{\sc Spark} acts as a situation assessment reasoner that generates symbolic
knowledge from the geometry of the environment with respect to relations between
objects, robots and humans. It also takes into account the different perspective
that each agent has on the environment. {\sc Spark} embeds a
modality-independent geometric model of the environment that serves both as
basis for the fusion of the perception modalities and as bridge with the
symbolic layer~\cite{lemaignan2016artificial}. This geometric model is built
from 3D CAD models of the objects, furnitures and robots, and full body, rigged
models of humans.  It is updated at run-time by the robot's sensors.
Likewise, \uwds embeds a grounded amodal model of the environment, updated
online from the robot's sensors (sensor fusion).

However, {\sc Spark} is a monolithic module, that does not support sharing its
internal 3D model to other external components. On the contrary, \uwds focuses
on offering a shared and distributed representation within the robot's software
architecture. Previous work on distributed scene graphs~\cite{naef2003blue} has
been applied to robotics to provide a shared 3D representation of the robot's
environment (like the \emph{Robot Scene Graph}~\cite{blumenthal2013scene} or 
\emph{Deep State Representation}~\cite{bustos2016unified} approaches).

\uwds further extends this line of work by providing the ability to manipulate
several \emph{alternative 3D worlds}, corresponding to filtered or hypothetical
\emph{views} on the perceived model of the environment.

>>>>

\author{Séverin Lemaignan$^{*}$, Fotios Papadopoulos$^{*}$%
\thanks{$^{*}$Authors are with Centre for Robotics and Neural Systems,
        Plymouth University, Plymouth PL48AA, United Kingdom
        {\tt\small firstname.surname@plymouth.ac.uk}}%
}

@@

\uwds is a distributed and lightweight open-source
framework\footnote{\url{https://github.com/severin-lemaignan/underworlds}} that
enables robot programmers to build and refine in real-time spatial and temporal
models of the environment surrounding a robot. \uwds makes it possible to share
these world models amongst the software components running on the robot.
Besides, \uwds permits to represent and manipulate in a distributed manner
\emph{multiple alternatives} to the current, perceived world model. For
instance, the world with some objects filtered out; the world `viewed' from the
perspective of another agent; an hypothetical world resulting from the simulated
application of a plan, etc.

\subsection{Distributed Situation Assessment}

@@

\uwds is specifically inspired by the geometric and temporal reasoner
{\sc Spark} (\emph{SPAtial Reasoning \& Knowledge})~\cite{sisbot2011situation}.
{\sc Spark} acts as a situation assessment reasoner that generates symbolic
knowledge from the geometry of the environment with respect to relations between
objects, robots and humans. It also takes into account the different perspective
that each agent has on the environment. {\sc Spark} embeds a
modality-independent geometric model of the environment that serves both as
basis for the fusion of the perception modalities and as bridge with the
symbolic layer~\cite{lemaignan2016artificial}. This geometric model is built
from 3D CAD models of the objects, furnitures and robots, and full body, rigged
models of humans.  It is updated at run-time by the robot's sensors.
Likewise, \uwds embeds a grounded amodal model of the environment, updated
online from the robot's sensors (sensor fusion).

However, {\sc Spark} is a monolithic module, that does not support sharing its
internal 3D model to other external components. In contrast, \uwds focuses on
offering a shared and distributed representation of the environment within the
robot's software architecture.

Work on distributed scene graphs~\cite{naef2003blue} has been previously applied
to robotics to provide a shared 3D representation of the robot's environment
(for instance, the \emph{Robot Scene Graph}~\cite{blumenthal2013scene} or the
\emph{Deep State Representation} proposed in~\cite{bustos2016unified}).  \uwds
offers a similar distribution mechanism for 3D scene graphs and extends it to
temporal representations. Besides, \uwds further extends this line of work by
providing the ability to create, manipulate and share \emph{multiple alternative
worlds}, corresponding for instance to filtered or hypothetical \emph{views} on
the initial, perceived model of the environment.
